Whats reported in the news?

### 2018-03-19 paper/docs/04_Modelresults_50.Rmd
finish that writing!

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

ggsave(filename = "../figs/ccf.png", plot = p,
       height = 6, width = 8)
```

>>>>

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[8], alpha = 0.8) +
  labs(x="", y="Number of articles") +
  theme(
    axis.text = element_text(size = 6),
      legend.position   = "none"
    )

@@

ggsave(filename = "../figs/ccf.png", plot = p,
       height = 6, width = 8, dpi = 600)
```
